Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-31 R0V0.tex
Add cholesky factor definition on notation

@@

\paragraph{Notation} Let $\mathbb{S}$ be a totally ordered set and $s_1,s_2,s_3\in\mathbb{S}$. The notation $\mathbb{S}_{[s_1,s_2)}$ (resp. $\mathbb{S}_{\diamond s_3}$) stands for the set $\{s\in\mathbb{S}:s_1\leq s< s_2\}$ (resp. $\{s\in\mathbb{S}:s\diamond s_3\}$, where $\diamond$ is a comparison operator, i.e., $\diamond\in\{<,\geq,=,\ \text{etc}\}$). Let $n>0$ be any integer, the vector $e_i$ denotes the vector with zeros in all rows except the $i$-th where it is 1. A matrix $M\in\mathbb{R}^{n\times n}$ with zero elements except (possibly) those  $m_{ii},\ldots,m_{nn}$ on the diagonal is denoted as $\mathbin{\mathtt{diag}}(m_{ii},\ldots,m_{nn})$. The notation $M\succ 0$ (resp. $M\succeq 0$) stands for $M$ being positive (resp. semi)definite.

@@

Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation}  cannot be done in parallel. The next section provides sufficient conditions to solve each component \eqref{eq:MI formulation} independently, and according to the structure defined by the set $\Xi$. Before presenting it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.

@@

Before showing how the MI \eqref{eq:MI formulation} can be computed in parallel, some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.

Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to a \emph{clique tree} and it is denote as $\mathscr{T}(\mathscr{G})$.

@@

>>>>

% *** ALGORITHM PACKAGES ***
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\paragraph{Notation} Let $\mathbb{S}$ be a totally ordered set and $s_1,s_2,s_3\in\mathbb{S}$. The notation $\mathbb{S}_{[s_1,s_2)}$ (resp. $\mathbb{S}_{\diamond s_3}$) stands for the set $\{s\in\mathbb{S}:s_1\leq s< s_2\}$ (resp. $\{s\in\mathbb{S}:s\diamond s_3\}$, where $\diamond$ is a comparison operator, i.e., $\diamond\in\{<,\geq,=,\ \text{etc}\}$). Let $n>0$ be any integer, the vector $e_i$ denotes the vector with zeros in all rows except the $i$-th where it is 1. A matrix $M\in\mathbb{R}^{n\times n}$ with zero elements except (possibly) those  $m_{ii},\ldots,m_{nn}$ on the diagonal is denoted as $\mathbin{\mathtt{diag}}(m_{ii},\ldots,m_{nn})$. The notation $M\succ 0$ (resp. $M\succeq 0$) stands for $M$ being positive (resp. semi)definite. For a matrix $M\succ0$, the notation $\mathbin{\mathtt{chol}}(M)$ stands for the \emph{upper-triangular Cholesky factor $U$} satisfying $A=U^\top U$.

@@

Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation} not has been said about the parallel compution of the MI~\eqref{eq:MI formulation}. The next section provides sufficient conditions to parallelize the search for a solution to the MI~ \eqref{eq:MI formulation}.

@@

For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem for the computation of a solution to the MI~\eqref{eq:MI formulation}. This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}. For this reason, the computation of a solution to MI~\eqref{eq:MI formulation} need to be done parallel. To this end some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.

Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denote as $\mathscr{T}(\mathscr{G})$.

@@

Although the decomposition of the MI~\eqref{eq:MI formulation} into smaller components can distribute the burden of computation. These components (matrices) may still have a large dimension. However, by employing an appropriate choice for the basis of squared polynomials, the dimension of the matrix can be smaller \cite{AhmadiHall2016}. To that end, the following class of matrices is recalled from \cite{AhmadiHall2016}.

\begin{definition}\label{def:}
	a
\end{definition}

\begin{algorithm}
        \caption{Some alg}
        \begin{algorithmic}[1]	
            \REQUIRE $U_0=I$
            \STATE d = a + b + c
            \STATE d = d/2
            \STATE d = d/3
            \RETURN d
        \end{algorithmic}
    \end{algorithm}
